Visualization of [fulle name] Fractional Integrals

### 2019-04-11 fractional/CMJ style files/article-template.tex
added examples of (y)$

@@

\section{Examples}
We use the geometric framework we presented in the previous paragraph to provide 
To make things clear we provide two fully worked examples below of how to geometrically interpret fractional integrals using conversion  presented in the previsous 
section. The two fractional integrals we will visualize are:\\

@@

The steps to visualize the above two integral wer described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
Riemann-Stieltjes integrals are then converted to Cavalieri integrals. The graphical

>>>>

\begin{table}[h!]
\centering
 \begin{tabular}{|c || c | c|} 
 \hline
 & \multicolumn{2}{|c|}{$a_{10}^{\alpha}(\tau)$}\\
 \hline
 &$f(\tau) = \tau$ & $f(\tau)=\sqrt{\tau}$ \\ [0.5ex] 
 \hline\hline
 $0$ & 0 & $y=0$ \\ 
 $0.2$ & $y-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y}\right)$ & $y^2-[\Gamma\left (\frac{6}{5} \right )]^{-1}\left(\sqrt[5]{10}-\sqrt[5]{10-y^2}\right)$  \\
 $0.4$ & $y-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y)^2}\right)$ & $y^2-[\Gamma\left (\frac{7}{5} \right )]^{-1}\left(\sqrt[5]{10^2}-\sqrt[5]{(10-y^2)^2}\right)$ \\
 $0.6$ & $y-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y)^3}\right)$ & $y^2-[\Gamma\left (\frac{8}{5} \right )]^{-1}\left(\sqrt[5]{10^3}-\sqrt[5]{(10-y^2)^3}\right)$ \\
 $0.8$ & $y-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y)^4}\right)$ & $y^2-[\Gamma\left (\frac{9}{5} \right )]^{-1}\left(\sqrt[5]{10^4}-\sqrt[5]{(10-y^2)^4}\right)$ \\ [1ex] 
 $1$ & $\tau$ & $\tau$ \\ [1ex] 
 \hline
 \end{tabular}
\end{table}

@@

\section{Examples}
In this section we will illustrate the usefulness of the proposed geometric framework at the hand of two examples.
Consider the two fractional integrals:

\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \tau(t-\tau)^{\alpha-1}~d\tau 
\end{equation}

and

\begin{equation}
\frac{1}{\Gamma(\alpha)}\int_0^t f(\tau) (t-\tau)^{\alpha-1}~d\tau = \frac{1}{\Gamma(\alpha)}\int_0^t \sqrt{\tau}(t-\tau)^{\alpha-1}~d\tau.
\end{equation}

@@

We can give

The steps to visualize the above two integrals were described in the previous paragraph. We first convert the integrals into Riemann-Stieltjes integrals. The 
Riemann-Stieltjes integrals are then converted to Cavalieri integrals. We can then simply depict the Cavalieri integrals and in doing so obtain a geometric interpretaion
of the original fractional integrals. Importantly, for each value of $t$ we obtain a different
